### 2017-05-22 paper/documents/1.introduction.tex
- update paper

This is Introduction also the related work.

>>>>

Computer games is a big business. competitive gaming growing the interest in this business. The competitive gaming events, the so-called electronic sports (sPorts). Multi-player online batle arena (MOBA) games are the most popular and succesful games in this regard. Game tournaments always give significant awards with big prize of money. Mostly, professional player can make a living from the prize. 
\\
In this paper we analyzing the player roles using supervised machine learning (ML) , investigate the applicability of feature normalization to enhance accuracy of prediction results. We also comparing our result with previous paper. Christoph Eggert on his paper said that their most stable and performing classifier is logistic regression. We will use the same classification method with their work. The different is we will using ROpenDota to built the data set.

### 2017-05-22 paper/documents/2.background.tex
- update paper

This is related work

>>>>

Dota2 is team based game in Multi-player Online Battle Arena (MOBA). Each team have five players. Every player will choose their hero in pre-match games. Currently, there is 113 heroes, 166 current items. Dota2 game design is separated the heroes with three types. The first is agility heroes type, the second is strength heroes type and the last is intelligent heroes type. Every heroes have own specialty and weakness. The items can be combine into upgrade-able item which is will give more status in heroes abilities.
\\
